---
title: "Dealing with Duplicates Workshop"
date: 2025-04-25
---

# Step 0: Load libraries

```{r include = FALSE}
library(tidyverse)
library(janitor)
library(assertr)
```


# Read in (fake) student data

```{r}
students <- read_rds("../Input/student_data.rds") 
```


Example: 

```{r}
students %>% get_dupes(student_id)
```


## How can you get_dupes with dplyr verbs?

Use the students dataset to get the dupes by student_id, without using `get_dupes()`

```{r}

```


# Correcting duplicates

## Method 1

Correct the dupes individually with if_else or case_when and then distinct to remove the straight dupes

```{r}
students_clean <- students %>% 
  mutate(grade = if_else(student_id == ..., ..., grade)) %>%
  distinct()

students_clean
```


## Method 2

Systematically remove dupes by taking the min or max of the duplicate
causing column

```{r}
students_clean <- students %>%
  group_by(student_id) %>% 
  summarize(grade = min(grade)) %>%
  ungroup()

students_clean
```


## Method 3

Flag the dupes individually with if_else or case_when, filter to them, and 
then anti_join them on.

```{r}
dupes_remove <- students %>% 
  mutate(remove = if_else(student_id == 6775709 & grade == 6, 1, 0)) %>%
  filter(remove == 1)

# anti_join the dupes on
students_clean <- anti_join(students, dupes_remove)
```


## Method 4

Output the duplicates, manually choose which version to remove,
and then anti_join those on

```{r}
# Write out the dupes
get_dupes(students, student_id) %>%
  write_csv(., "../QC/student_id_dupes.csv", na = "")

# Open the file in Excel, add a column called remove with a 0 or flag
# to indicate whether or not you should remove it from the dataset
# Then save it as student_id_dupes_corrected.csv in the Input folder

# Read in the annotated file
# Filter to the row(s) you want to remove
dupes_remove <- read_csv("../Input/student_id_dupes_corrected.csv") %>% 
  filter(remove == 1) %>%
  # Fix columns that don't match the rds after reading it in as a csv
  mutate(student_id = as.character(student_id),
         across(contains("date"), mdy))

# anti_join the dupes on
students_clean  <- anti_join(students, dupes_remove)
```


# YOU DO! 

```{r}
practice_exam <- read_csv("../Input/practice_exam.csv")

practice_exam
```

## Find duplicates in the Practice Exam data

* Take a look at the data.  What do you think the data is/should be unique by?
* Are there dupes? How many? What are they by?
* What business rule do you think you should apply to correct these duplicates?

```{r}
practice_exam %>% 
  get_dupes(student_number, subject)
```


## Correcting duplicates in the Practice SAT data

Correct the duplicates in the Practice SAT data by only keeping the rows where
the exam grade matches the student’s grade level.
Check that there are no dupes in your corrected data.

Name your tibble of dupes dupes_remove

```{r}

```


